A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-24 paper/paper.Rnw
Another stab at concluding

A larger difficulty is the inherent overlap between features of common geometric shapes, and high variability of those shapes on outsoles. Overlapping features between shapes makes it more difficult for the model to distinguish between geometrically similar shapes, such as chevrons and triangles. When the physical shapes present within a category are highly variable, this further widens the sets of features associated with individual categories, leading to even more model confusion. These issues of overlap and variabailty are at least in part due to the features used by practitioners, and partially due to our generalization/operational definition.}

\mt{What is the balance between comprehensive and redundant? I don't think I've found it... I'll try again when not exhausted}

\mt{Final paragraph will suggest redefining shapes (yuck) and cutting off the final conv block to see whether those features are easier for the model to sort between categories.}

>>>>

A larger difficulty is the inherent overlap between features of common geometric shapes; since CNNs make predictions via bottom-up feature integration, it is more difficult for the model to distinguish between geometrically similar shapes, such as chevrons and triangles. This issue is exacerbated by high variability of those shapes on outsoles, which requires the model to form a flexible understanding of  each shape category, but makes distinction even more difficult. These issues of overlap and variabailty are at least in part due to the features used by practitioners, and partially due to the operational definitions of each class used in this research. While a \fix{full} remedy may not be possible, there may be some modifications to operational class definitions that we can make to optimize labels for model prediction.}
